\begin{enumerate}
    The term Machine Learning was coined by Arthur Samuel in 1959, an American pioneer in the field of computer gaming and artificial intelligence and stated that \say{it gives computers the ability to learn without being explicitly programmed.}
And in 1997, Tom Mitchell gave a \say{well-posed} mathematical and relational definition that \say{A computer program is said to learn from experience E with respect to some task T and some performance measure P, if its performance on T, as measured by P, improves with experience E.}

    To understand Machine Learning in layman terms, consider you are trying to toss a paper to a dustbin. After first attempt, you realize that you have put too much force in it. After second attempt, you realize you are closer to target but you need to increase your throw angle. What is happening here is basically after every throw we are learning something and improving the end result. We are programmed to learn from our experience.

This implies that the tasks in which machine learning is concerned offers a fundamentally operational definition rather than defining the field in cognitive terms. The question \SAY{Can machines think?} is replaced with the question \say{Can machines do what we (as thinking entities) can do?}
Within the field of data analytics, machine learning is used to devise complex models and algorithms that lend themselves to prediction; in commercial use, this is known as predictive analytics. These analytical models allow researchers, data scientists, engineers, and analysts to \say{produce reliable, repeatable decisions and results} and uncover \say{hidden insights} through learning from historical relationships and trends in the data set(input).

\end{enumerate}