\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}

%Giving a short overview of the work in your project.
Emerging technologies and programming techniques increase our ability to create
intelligent software programs. With the advent of viable neural networking solutions, we
have come even closer to building artificially intelligent machines. This project outlines
the impact of neural networking on the development of artificial intelligence (AI)
systems, explores the impact of AI systems on society, and proposes enhanced ethical
and professional roles for artificial intelligence developers, with an emphasis on
interpersonal communication and impact awareness.\\
The projections discussed here are provided both by technology experts and
concerned non-experts. Computer systems will continue to get more powerful, and will
become increasingly ubiquitous in the future, making the standards of development of
artificial intelligence a salient topic in modern engineering. Despite a socially ingrained
fear of intelligent machines, there is no governing body to oversee the continued
development of AI systems.\\
Development of a strong artificial intelligence would surely call into question (for some)
that which we define as “alive.” It is yet unclear whether an electronic entity would be
entitled to legal and civil rights. Furthermore, we do not know whether such an entity or
race of entities would be dangerous to society. These problems indicate a strong ethical
component in the development of intelligent software. This paper argues that intelligent
machines will be intertwined in our future society, and addresses the lack of a concrete
body to govern the development of computer software. The accompanying research
further establishes that engineers will have increased ethical and political responsibilities
in the development of artificial intelligence systems in the future.

\end{abstract}